A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-24 paper/draft.tex
partisanship

\subsection{Wealthy Patrons}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width = 7cm, height = 8cm]{figures/partisanship/plot_edu_mean.pdf}
    \includegraphics[width = 7cm, height = 8cm]{figures/partisanship/plot_age_mean.pdf}
    \caption{\textbf{Heterogeneity in Education and Age.}}
    \label{fig:partisan_edu_et_age}
\end{figure}

@@

Party members are relatively concentrated in high level bureaucrat positions, such as managers and directors. These are also the best

>>>>

\subsection{Who enters the bureaucracy?}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width = 7cm, height = 8cm]{figures/partisanship/plot_edu_mean.pdf}
    \includegraphics[width = 7cm, height = 8cm]{figures/partisanship/plot_age_mean.pdf}
    \caption{\textbf{Heterogeneity in Education and Age.} Party members tend to be less educated and older than their non-partisan counterparts.}
    \label{fig:partisan_edu_et_age}
\end{figure}

This empirical record suggests important dynamics occurring in the selection phase of the bureaucracy: who enters the public sector. Another important question is once these party members enter the bureaucracy, where do they go to. The next section explores empirical regularities with respect to the concentration of party members once they are in the local bureaucracies, or islands of patronage.

@@

Party members are relatively concentrated in high level bureaucrat positions, such as managers and directors. These are also the best paying positions and the ones with the highest proportion of career protection in the form of contract tenure (\emph{estatutário}). Moving down the hierarchy, it is clear that party members predominantly occupy high level positions, in particular staying at the
